---
title: "Report"
author: "Grupo6"
date: "6/3/2021"
output: rmdformats::material
---
# Introduction
For the making of this report, it was given a dataset with data of pacients of the Hospital Austral who had suffered from heart diseases and where treated there with a surgery or an angioplasty. So, the goal of this report is trying to predict the neccesary intervention a future pacient may need.

```{r,echo=FALSE,message=FALSE}
dataset <- read.csv("dataset.csv", sep=",")
library(ggplot2)
library(plotrix)
library(hrbrthemes)
library(dplyr)
library(tidyr)
```

# Analysis
In this section, we are going to analyze the different factors and variables that may be used to take into account in the predictor

## Gender
Gender
```{r,echo=FALSE,message=FALSE}
numOfMale <- length(dataset$SEXO[which(dataset$SEXO == "MASC")])
numOfFemale <- length(dataset$SEXO[which(dataset$SEXO == "FEME")])
totalNum <- numOfFemale + numOfMale
percentageOfMale <- round(numOfMale / totalNum * 100, 2)
percentageOfFemale <- round(numOfFemale / totalNum * 100, 2)
percentages <- c(percentageOfFemale,percentageOfMale)

#Pie
pie3D(percentages,main = "Porcentaje de Hombres y Mujeres", labels = c(paste("Mujeres", percentageOfFemale,"%"), paste("Hombres", percentageOfMale,"%")), theta = 1, explode = 0.00)


ageAverageInMen <- mean(dataset[which(dataset$SEXO == "MASC"),]$EDAD)
ageAverageInWomen <- mean(dataset[which(dataset$SEXO == "FEME"),]$EDAD)

ages <- c(dataset[which(dataset$SEXO == "MASC"),]$EDAD,dataset[which(dataset$SEXO == "FEME"),]$EDAD)


```

# Interpretation
We interpretate the graphs and put more y data ...